Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-24 main.Rmd
content cut - section 2 - iteration 2

@Bettini1998-ed discusses the relationships between linear time granularities, the structure of a calendar, and periodicities in time.

@@

A discrete time model often uses a fixed smallest granularity also known as *_bottom granularity_* (@Bettini1998-ed) so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called *_chronons_* (@Jensen1998-qn). Chronons may be grouped into granules and a non-overlapping mapping of granules to subsets of the time domain is a linear granularity. A system of multiple granularities in lattice structures is referred to as a *_calendar_* (see @Dyreson2000-mr).

>>>>

@Bettini1998-ed discusses the relationships between linear time granularities, periodicities in time, and the structure of a calendar.

@@

A discrete time model often uses a fixed smallest granularity also known as _bottom granularity_ (@Bettini1998-ed) so that the the underlying time domain can be described as a sequence of non-decomposable, consecutive time intervals of some fixed, minimal duration called _chronons_ (@Jensen1998-qn). Chronons may be grouped into granules and a non-overlapping mapping of granules to subsets of the time domain is a linear granularity. A system of multiple granularities in lattice structures is referred to as a _calendar_ (see @Dyreson2000-mr).
